Title

### 2018-08-01 thesis/paper/paper.tex
Added single value

>>>>

\subsection{Single value (Q19474404)}
The single value constraint can be divided into two different cases, depending on if the set of separators \(S\) is empty or not. Pre-processing needs to extract all item statements and their qualifiers and establish inequality between all statement IDs and all qualifier values.

\subsubsection{No separators}
If the separator set is empty, the violation simply occurs if there are two constrained statements on the same item. 
\begin{equation}\label{eq_no_separators_triple}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{unequal}(S, O)
\end{split}
\end{equation}
For qualifiers and reference there is no ID whose inequality could be checked. However, since the statement ID and the property of a possible conflict are always the same, inequality can be tested on the values.
\begin{equation*}
\begin{split}
\text{violation\_qualifier}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \\
&\text{qualifierEDB}(S, \text{propertyConstant}, X) \wedge \\
&\text{unequal}(V, X)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{violation\_reference}&(S, \text{propertyConstant}, V) \leftarrow \\
&\text{referenceEDB}(S, \text{propertyConstant}, V) \wedge \\
&\text{referenceEDB}(S, \text{propertyConstant}, X) \wedge \\
&\text{unequal}(V, X)
\end{split}
\end{equation*}
\todo{Check if all reference-rules look exactly like the qualifier rules and cut them out if it is so.}

\subsubsection{With separators}
To find all violations under separators a number of things have to be considered. Only triples are eligible, since qualifiers cannot have further qualifier, and the order of qualifiers on constrained statements needs to be pre-processed as well since qualifier non-existence is relevant. The predicate require\([4]\) is introduced which notes the statement ID, property, and value of a qualifier as well as the separator. The pattern needs to be applied for every separator, meaning the conjunction is: \(t = \text{qualifierEDB}(S, P, V) \wedge \text{unequal}(P, \text{requiredPropertyConstant})\) for each separator in \(S\).\\

With qualifier non-existence established the violation can be found. Two statements form a violation if they are distinct as per equation \ref{eq_no_separators_triple} and additionally fulfil the condition that all qualifiers are either equal or non-existent. \(\forall X \subset S, Y = S \setminus X\) the following rule has to be added. Note that \(qualifierEDB(S, {X}, [X])\) denotes one atom for each element \(x \in X\) as introduced in section \ref{subsec_allowed_units} with \([X]\) representing a variable which is distinct for each atom unless they have the same \(x\). With the predicate does\_not\_have\([2]\) linking a statement ID to the separator it does not have via \(\text{does\_not\_have}(S, R) \leftarrow \text{last\_qualifier}(S, P, V) \wedge \text{require}(S, P, V, R)\) for brevity the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, I, \text{propertyConstant}, W) \wedge \\
&\text{unequal}(S, O) \wedge \\
&\text{qualifierEDB}(S, \{X\}, [X]) \wedge \\
&\text{qualifierEDB}(O, \{X\}, [X]) \wedge \\
&\text{does\_not\_have}(S, \{Y\}) \wedge \\
&\text{does\_not\_have}(O, \{Y\})
\end{split}
\end{equation*}
